\documentclass[a4paper]{article}
\nonstopmode
\usepackage{a4wide}
\usepackage{makeidx}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{float}
\usepackage{alltt}
\usepackage{doxygen}
\usepackage{times}
\ifx\pdfoutput\undefined
\usepackage[ps2pdf,
            pagebackref=true,
            colorlinks=true,
            linkcolor=blue
           ]{hyperref}
\else
\usepackage[pdftex,
            pagebackref=true,
            colorlinks=true,
            linkcolor=blue
           ]{hyperref}
\fi
\usepackage{purrs}
\makeindex
\setcounter{tocdepth}{1}
\setlength{\footrulewidth}{0.4pt}

\rfoot[\fancyplain{}{\scriptsize The Parma University's Recurrence Relation Solver Developer's Manual (version $projectnumber). See \url{http://www.cs.unipr.it/purrs/} for more information.}]{}
\lfoot[]{\fancyplain{}{\scriptsize The Parma University's Recurrence Relation Solver Developer's Manual (version $projectnumber). See \url{http://www.cs.unipr.it/purrs/} for more information.}}

\begin{document}
\title{
The Parma University's Recurrence Relation Solver \\
Developer's Manual\thanks{This work
  has been partly supported by:
  University of Parma's FIL scientific research project (ex 60\%)
    ``Pure and Applied Mathematics'';
  MURST project
    ``Automatic Program Certification by Abstract Interpretation'';
  MURST project
    ``Abstract Interpretation, Type Systems and Control-Flow Analysis''.
  } \\
(version $projectnumber)
}
\author{
Roberto Bagnara\thanks{bagnara@cs.unipr.it,
  Department of Mathematics, University of Parma, Italy.} \\
Patricia M. Hill\thanks{hill@comp.leeds.ac.uk,
  School of Computing, University of Leeds, U.K.} \\
Elisa Ricci\thanks{ericci@cs.unipr.it,
  Department of Mathematics, University of Parma, Italy.} \\
Enea Zaffanella\thanks{zaffanella@cs.unipr.it,
  Department of Mathematics, University of Parma, Italy.} \\
\ \\
based on previous work also by \\
\ \\
Sara Bonini		\\
Andrea Pescetti		\\
Angela Stazzone		\\
Tatiana Zolo\thanks{zolo@cs.unipr.it,
  Department of Mathematics, University of Parma, Italy.}
}
\maketitle

\newpage
Copyright \copyright\ 2001 Roberto Bagnara (bagnara@cs.unipr.it).

This document describes the Parma Polyhedra Library (PPL).

Permission is granted to copy, distribute and/or modify this document
under the terms of the GNU Free Documentation License, Version 1.1 or
any later version published by the
\href{http://www.fsf.org}{Free Software Foundation}; with no Invariant
Sections, with no Front-Cover Texts, and with no Back-Cover Texts.
A copy of the license is included in the section entitled
``\hyperlink{GFDL}{GNU Free Documentation License}''.

The PPL is free software; you can redistribute it and/or modify it
under the terms of the GNU General Public License as published by the
\href{http://www.fsf.org}{Free Software Foundation}; either version 2
of the License, or (at your option) any later version.
A copy of the license is included in the section entitled
``\hyperlink{GPL}{GNU GENERAL PUBLIC LICENSE}''.

The PPL is distributed in the hope that it will be useful, but WITHOUT
ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or
FITNESS FOR A PARTICULAR PURPOSE.  See the GNU General Public License
for more details.

For the most up-to-date information see the PURRS WWW site:
\begin{center}
\href{http://www.cs.unipr.it/ppl/}{\tt http://www.cs.unipr.it/purrs/}
\end{center}

\pagenumbering{roman}
\tableofcontents
\pagenumbering{arabic}
